---
title: "Full Tutorial"
author: "Exceret"
date: '`r Sys.Date()`'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Full Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# **Full Tutorial for SigBridgeR** {#full-tutorial-for-sigbridger}

## 0. Preface

### 0.1 Contents

- [**Full Tutorial for SigBridgeR** {#full-tutorial-for-sigbridger}](#full-tutorial-for-sigbridger-full-tutorial-for-sigbridger)
  - [0. Preface](#0-preface)
    - [0.1 Contents](#01-contents)
    - [0.1 Introduction to SigBridgeR](#01-introduction-to-sigbridger)
  - [1. Installation](#1-installation)
    - [1.1 Stable Release from GitHub](#11-stable-release-from-github)
    - [1.2 Check Dependencies](#12-check-dependencies)
  - [2. Loading and preprocessing data](#2-loading-and-preprocessing-data)
    - [2.1 Single-cell RNA-seq Data](#21-single-cell-rna-seq-data)
      - [2.1.1 (Option A) Start from Raw Matrix](#211-option-a-start-from-raw-matrix)
      - [2.1.2 (Option B) Start from AnnDataR6 Object](#212-option-b-start-from-anndatar6-object)
      - [2.1.3 (Optional) Filter Out Tumor Cells](#213-optional-filter-out-tumor-cells)
    - [2.2 Bulk expression data](#22-bulk-expression-data)
      - [2.2.1 Evaluate the quality of your bulk RNA-seq data](#221-evaluate-the-quality-of-your-bulk-rna-seq-data)
        - [Quality Control Metrics Reported: {#quality-control-metrics-reported}](#quality-control-metrics-reported-quality-control-metrics-reported)
        - [Visualization Output: {#visualization-output}](#visualization-output-visualization-output)
        - [Recommended Parameter Adjustments: {#recommended-parameter-adjustments}](#recommended-parameter-adjustments-recommended-parameter-adjustments)
      - [2.2.2 Gene Symbol Conversion](#222-gene-symbol-conversion)
    - [2.3 Phenotype Data](#23-phenotype-data)
  - [3. Screening Cells Associated with Phenotype](#3-screening-cells-associated-with-phenotype)
    - [3.1 (Option A) Scissor Screening](#31-option-a-scissor-screening)
    - [3.2 (Option B) scPAS Screening](#32-option-b-scpas-screening)
    - [3.3 (Option C) scAB Screening](#33-option-c-scab-screening)
    - [3.4 (Option D) scPP Screening](#34-option-d-scpp-screening)
    - [3.5 (Optional) Merge screening results](#35-optional-merge-screening-results)
  - [4. Visualization](#4-visualization)
    - [4.1 UMAP for screening results](#41-umap-for-screening-results)
    - [4.2 Stack bar plot for screening results](#42-stack-bar-plot-for-screening-results)
    - [4.3 Venn diagram for screening results](#43-venn-diagram-for-screening-results)
  - [5. Example {#example}](#5-example-example)
  - [6. Other function details](#6-other-function-details)
    - [6.1 Add miscellaneous information to the Seurat object](#61-add-miscellaneous-information-to-the-seurat-object)
    - [6.2 Calculate the variance of each row in a matrix](#62-calculate-the-variance-of-each-row-in-a-matrix)
  - [7. References](#7-references)

### 0.1 Introduction to SigBridgeR

SigBridgeR (short for **Sig**nificant cell-to-phenotype **Bridge** in **R**) is an R package for screening cells highly associated with phenotype data using single-cell RNA-seq, bulk expression and sample_related phenotype data at a pan-cancer level. It integrates functionality from these R packages: [Github-sunduanchen/Scissor](https://github.com/sunduanchen/Scissor), [Github-Qinran-Zhang/scAB](https://github.com/Qinran-Zhang/scAB/), [Github-WangX-Lab/ScPP](https://github.com/WangX-Lab/ScPP) and [Github-aiminXie/scPAS](https://github.com/aiminXie/scPAS).

------------------------------------------------------------------------

## 1. Installation

Install **SigBridgeR** using one of these methods:

### 1.1 Stable Release from GitHub

```{r install_from_github}
if(!requireNamespace("remotes")) {
  install.packages("remotes")
}
remotes::install_github("WangLabCSU/SigBridgeR")
```

### 1.2 Check Dependencies

You can use this function to quickly verify installed dependencies and their versions:

```{r check_dependencies}
CheckPkgs <- function(packages) {
  CheckSinglePkg <- function(pkg_spec) {
    installed <- requireNamespace(pkg_spec$pkg, quietly = TRUE)
    current_version <- NA_character_
    
    if (installed) {
      current_version <- as.character(utils::packageVersion(pkg_spec$pkg))
      
      if (!is.null(pkg_spec$version)) {
        installed <- current_version >= pkg_spec$version
      }
    }
    
    data.frame(
      Package = pkg_spec$pkg,
      Required_Version = if (is.null(pkg_spec$version)) "Any" else pkg_spec$version,
      Installed = installed,
      Current_Version = if (installed) current_version else NA,
      stringsAsFactors = FALSE
    )
  }
  
  result <- do.call(rbind, lapply(packages, CheckSinglePkg))
  rownames(result) <- NULL  
    
  return(result)
}

CheckPkgs(list(
  list(pkg = "Seurat", version = "5.0.0"),
  list(pkg = "dplyr"),
  list(pkg = "cli"),
  list(pkg = "AUCell", version = "1.20.2"),
  list(pkg = "future"),
  list(pkg = "ggrepel"),
  list(pkg = "grid"),
  list(pkg = "IDConverter"),
  list(pkg = "Matrix"),
  list(pkg = "patchwork"),
  list(pkg = "scAB"),
  list(pkg = "Scissor"),
  list(pkg = "scPAS"),
  list(pkg = "ScPP"),
  list(pkg = "tibble"),
  list(pkg = "tidyr"),
  list(pkg = "data.table", version = "1.14.1")
  )
)

```

------------------------------------------------------------------------

## 2. Loading and preprocessing data

First load the package:

```{r load_package}
library(SigBridgeR)
```

### 2.1 Single-cell RNA-seq Data

You can use function `SCPreProcess` to preprocess your single-cell RNA-seq data. Here are some options:

#### 2.1.1 (Option A) Start from Raw Matrix

When starting from a raw count matrix, `SCPreProcess` will automatically perform Seurat preprocess (including `NormalizeData, FindVariableFeatures, ScaleData, RunPCA, FindNeighbors, FindClusters, RunTSNE, RunUMAP`). `SCPreProcess` returns a fully preprocessed Seurat object for downstream use.

```{r scpreprocessing_raw_matrix}
your_seurat <- SCPreProcess(
  your_matrix,
  project = "Scissor_Single_Cell", # Parameters used in Seurat preprocessing pipeline
  min_cells = 400,
  min_features = 0,
  normalization_method = "LogNormalize",
  scale_factor = 10000,
  selection_method = "vst",
  resolution = 0.6,
  dims = 1:10,
  verbose = TRUE,
  future_global_maxsize = 6 * 1024^3,
  ...
)
```

#### 2.1.2 (Option B) Start from AnnDataR6 Object

`SCPreProcess` also supports AnnData objects. You may reference and use the following code:

```{r scpreprocessing_anndata}
reticulate::use_pythonenv("The_path_to_your_python") 

anndata_obj <- anndata::read_h5ad("path_to_your_file.h5ad") # Or other formats

your_seurat <- SCPreProcess(
  anndata_obj,
  project = "Scissor_Single_Cell", # Parameters used in Seurat preprocessing pipeline
  min_cells = 400,
  min_features = 0,
  normalization_method = "LogNormalize",
  scale_factor = 10000,
  selection_method = "vst",
  resolution = 0.6,
  dims = 1:10,
  verbose = TRUE,
  future_global_maxsize = 6 * 1024^3,
  ...
)
```

The description of data in `anndata_obj$obs` will be add to `your_seurat@meta.data`.

**helpful documentation:**

-   [AnnData for R](https://github.com/dynverse/anndata)

#### 2.1.3 (Optional) Filter Out Tumor Cells

If you aim to filter out phenotype-associated cells in all tumor cells. With a preprocessed Seurat object (containing results from ), `SCPreProcess` will filter out tumor cells using the specified metadata column:

```{r scpreprocessing_seurat}
your_seurat <- SCPreProcess(your_seurat, column2only_tumor = "Tissue")
```

> Note: I don't recommend using columns like `column2only_tumor = "Celltype"` as tumor cell identities vary across tissues. instead:
>
> -   Create a Dedicated Column: Add a new metadata column (e.g., is_tumor) to explicitly label cells:"Tumo(u)r"/"Normal"
>
> -   Code Example:
>
> ```{r }
> # For glioblastoma (GBM)
> seurat_obj@meta.data$is_tumor <- ifelse(
>  grepl("GBM|glioblastoma|astrocytoma_grade_IV", seurat_obj@meta.data$Celltype, ignore.case = TRUE),
>  "Tumor",  # or "Tumour" 
>  "Normal"  # or "Non-Tumor" 
> )
> ```

### 2.2 Bulk expression data

#### 2.2.1 Evaluate the quality of your bulk RNA-seq data

`BulkPreProcess` performs comprehensive quality control on bulk RNA-seq data.

Key parameters for `BulkPreProcess`:

-   `data`: Expression matrix with genes as rows and samples as columns, or a list containing count_matrix and sample_info.
-   `sample_info`: Sample information data frame (optional), ignored if data is a list.
-   `gene_symbol_conversion`: Whether to convert Ensembl version IDs and TCGA version IDs to genes with [SymbolConvert](#222-gene-symbol-conversion), default TRUE.
-   `check`: Whether to perform detailed quality checks, default TRUE.
-   `min_count_threshold`: Minimum count threshold for gene filtering, default 10.
-   `min_gene_expressed`: Minimum number of samples a gene must be expressed in, default 3.
-   `min_total_reads`: Minimum total reads per sample, default 1e6.
-   `min_genes_detected`: Minimum number of genes detected per sample, default 10000.
-   `min_correlation`: Minimum correlation threshold between samples, default 0.8.
-   `n_top_genes`: Number of top variable genes for PCA analysis, default 500.
-   `show_plot_results`: Whether to generate PCA visualization plots, default TRUE.
-   `verbose`: Whether to output detailed information, default TRUE.

Suppose you have bulk RNA-seq count data and sample information, and you want to perform comprehensive preprocessing and quality control. You can refer to and use the following code:

```{r bulk_preprocess_example}
# Example usage of BulkPreProcess
filtered_counts <- BulkPreProcess(
   data = your_count_matrix,
   sample_info = your_sample_info,
   gene_symbol_conversion = TRUE,
   check = TRUE,
   min_count_threshold = 10,
   min_samples_expressed = 3,
   min_total_reads = 1e6,
   min_genes_detected = 10000,
   min_correlation = 0.8,
   n_top_genes = 500,
   show_plot_results = TRUE,
   verbose = TRUE
)
```

The function returns a filtered count matrix after applying quality control steps. The order of filtering is: first genes, then samples.

##### Quality Control Metrics Reported: {#quality-control-metrics-reported}

-   Data Integrity: Number of missing values detected

-   Gene Count: Total number of genes after filtering

-   Sample Read Depth: Total reads per sample

-   Gene Detection Rate: Number of genes detected per sample

-   Sample Correlation: Pearson correlation between samples

-   PCA Variance: Variance explained by first two principal components

-   Batch Effects: Proportion of genes significantly affected by batch

##### Visualization Output: {#visualization-output}

When `show_plot_results = TRUE`, the function generates:

PCA plot colored by experimental condition

##### Recommended Parameter Adjustments: {#recommended-parameter-adjustments}

-   For low-depth sequencing data: reduce `min_total_reads` and `min_genes_detected`

-   For noisy datasets: increase `min_correlation` threshold

-   For large datasets: set `check = FALSE` for faster processing

Use `?BulkPreProcess` in R to see more details.

#### 2.2.2 Gene Symbol Conversion

`SymbolConvert` performs a straightforward task: converting common gene identifiers (e.g., Ensembl IDs, Entrez) to standardized gene symbols by using the [IDConverter](https://github.com/ShixiangWang/IDConverter) package.

```{r symbol_convert_example}
# genes * samples
your_bulk_data <- read.csv("path_to_your_file.csv", header = TRUE, row.names = 1)

your_bulk_data <- SymbolConvert(your_bulk_data)
```

You can also use the `org.Hs.eg.db` package for gene symbol matching if you prefer not to use SymbolConvert's built-in `IDConverter`.

```{r symbol_convert_example2}
library(org.Hs.eg.db)

your_bulk_data <- read.csv("path_to_your_file.csv", header = TRUE, row.names = 1)

your_bulk_data <- BulkPreProcess(your_bulk_data, gene_symbol_conversion = FALSE)

ensembl_ids <- sub("\\..*", "", rownames(your_bulk_data))
gene_symbols <- mapIds(org.Hs.eg.db, 
                      keys = ensembl_ids,
                      column = "SYMBOL",
                      keytype = "ENSEMBL",
                      multiVals = "first")

rownames(your_bulk_data) <- gene_symbols
your_bulk_data <- your_bulk_data[!is.na(rownames(your_bulk_data)), ]

```

### 2.3 Phenotype Data

bascially you can just use your phenotype data directly. If you are confused about the structure `Screen()` requires, please refer to [Section 5](#example).

------------------------------------------------------------------------

## 3. Screening Cells Associated with Phenotype

The function **`Screen`** provide 4 different options for screening cells associated with phenotype, These 4 algorithms come from the repositories mentioned in [Section 0.1](#01-introduction-to-sigbridger), and you can choose one of them to screen your cells.

Key parameters for `Screen`:

-   `matched_bulk`: A data frame of bulk expression data after intersecting samples.
-   `sc_data`: A Seurat object after preprocessing, you can use the output of `Preprocess` function or your own preprocessed Seurat object.
-   `phenotype`: A data frame of phenotype data after intersecting samples.
-   `label_type`: A character value specifying the filtering labels are stored in the `Seurat_object@misc` , default: `NULL`.
-   `phenotype_class`: A character value specifying the phenotype data type, i.e. `"binary"`, `"survival"` or `"continuous"`.
-   `screen_method`: A character value specifying the screening method, i.e. "Scissor", "scPAS", "scAB" or "scPP"
-   `...`: Other parameters for the screening methods.

### 3.1 (Option A) Scissor Screening

Parameters pass to `...` when using `Scissor` method:

-   `path2save_scissor_inputs`: A character value specifying the path to save intermediate data, default: `Scissor_inputs.RData`
-   `path2load_scissor_cahce`: A character value specifying the path to load intermediate data
-   `scissor_alpha`: Parameter used to balance the effect of the l1 norm and the network-based penalties. It can be a number or a searching vector. If alpha = NULL, a default searching vector is used. The range of alpha is in `[0,1]`. A larger alpha lays more emphasis on the l1 norm.
-   `scissor_cutoff`: Cutoff for the percentage of the Scissor selected cells in total cells. This parameter is used to restrict the number of the Scissor selected cells. A cutoff less than 50% (default 20%) is recommended depending on the input data.
-   `reliability_test_alpha`: the same as `scissor_alpha`
-   `reliability_test_n`: Permutation times (default: 10)
-   `nfold`: The fold number in cross-validation (default: 10)

**Usage**:

```{r scissor_screening}
scissor_result = Screen(
  matched_bulk = matched_bulk,
  sc_data = sc_dataset, # A Seurat object after preprocessing
  phenotype = matched_phenotype_data,
  label_type = "TP53", # The filtering labels are stored in the `@misc` 
  phenotype_class = "binary",  
  screen_method = c("Scissor"),
  path2save_scissor_inputs = "Tmp/Scissor_inputs.RData" # Intermediate data
)
```

You can use the intermediate data for repeated runs. This is an inherent feature of the `scissor`.

```{r scissor_screening_cache}
scissor_result = Screen(
  sc_data = sc_dataset, 
  label_type = "TP53", 
  phenotype_class = "binary", 
  screen_method = c("Scissor"),
  path2load_scissor_cahce = "Tmp/Scissor_inputs.RData" # Intermediate data
  path2save_scissor_inputs = "Tmp/Scissor_inputs.RData" 
)
```

If only the parameters `scissor_alpha` and `scissor_cutoff` are adjusted, this method can also be applied.

```{r scissor_screening_param_adjusted}
scissor_result = Screen(
  label_type = "TP53", 
  phenotype_class = "binary", 
  screen_method = c("Scissor"),
  path2load_scissor_cahce = "Tmp/Scissor_inputs.RData", # Intermediate data
  scissor_alpha = 0.05, 
  scissor_cutoff = 0.05 
)

```

**Returning structure**: A list containing:

-   `scRNA_data`: A Seurat object after screening
-   `scissor_result`: The result of Scissor screening
-   `reliability_test`: Reliability test results

**Cell level Evaluation**:

You can use `Sissor::evaluate.cell()` to obtain some supporting information for each Scissor selected cell. First, prepare a benchmark data set.

```{r scissor_screening_cell_level_evaluation}
evaluate_summary <- Scissor::evaluate.cell(
    './data/benchmark_data.RData',
    scissor_result$scissor_result,
    FDR = 0.05,
    bootstrap_n = 100
)
```

helpful documentation:

[Scissor-Cell Level Evaluations](https://sunduanchen.github.io/Scissor/vignettes/Scissor_Tutorial.html#cell-level-evaluations)

### 3.2 (Option B) scPAS Screening

Parameters pass to `...` when using `scPAS` method (basically adapted from the `scPAS`'s documentation):

-   Parameters passed to `scPAS::scPAS()`

    These parameters directly interface with the core `scPAS`() function from the original package:

    -   `assay`: Name of Assay to get.
    -   `imputation`: Logical. imputation or not.
    -   `nfeature`: Numeric. The Number of features to select as top variable features in `sc_data`. Top variable features will be used to intersect with the features of `matched_bulk`. Default is NULL and all features will be used.
    -   `alpha`: Numeric. Parameter used to balance the effect of the l1 norm and the network-based penalties. It can be a number or a searching vector. If `alpha = NULL`, a default searching vector is used. The range of alpha is in `[0,1]`. A larger alpha lays more emphasis on the l1 norm.
    -   `network_class`: The source of feature-feature similarity network. By default this is set to sc and the other one is bulk.

-   Parameters passed to `SigBridgeR::DoscPAS`

    These parameters represent customizable options provided by upstream/downstream processing functions when integrating the `scPAS` workflow

    -   `extra_filter`: A logical value. If `TRUE`, the following options for filtering will be applied. Default is `FALSE`.
    -   `gene_RNAcount_filter`: A numeric value. The threshold for filtering out genes with low RNA counts. Default is `20`.
    -   `bulk_0_filter_thresh`: A numeric value. The threshold for filtering out samples with low RNA counts. Default is `0.05`.

**usage**:

```{r scPAS_screening}
scpas_result = Screen(
  matched_bulk = matched_bulk,
  sc_data = A_Seurat_object,
  phenotype = phenotype,
  label_type = "TP53", # The filtering labels are stored in the `@misc` 
  screen_method = "scpas",
  phenotype_class = "binary"
)
```

**returning structure**: A list containing:

-   `scRNA_data`: A Seurat object after screening

### 3.3 (Option C) scAB Screening

Parameters pass to `...` when using `scAB` method (basically adapted from the `scAB`'s documentation):

-   `alpha`: Coefficient of phenotype regularization, default is `0.005`
-   `alpha_2`: Coefficient of cell-cell similarity regularization, default is `5e-05`
-   `maxiter`: Maximum number of iterations, default is `2000`
-   `tred`: Threshold for early stopping, default is `2`

**usage**:

```{r scAB_screening}
scab_result = Screen(
  matched_bulk = your_matched_bulk,
  sc_data = A_Seurat_object,
  phenotype = your_matched_phenotype,
  label_type = "TP53", # The filtering labels are stored in the `@misc` 
  screen_method = "scAB",
  phenotype_class = "binary",
)
```

**returning structure**: A list containing:

-   `scRNA_data`: A Seurat object after screening
-   `scAB_result`: A list with the submatrix and loss value

### 3.4 (Option D) scPP Screening

Parameters pass to `...` when using `scPP` method :

-   `ref_group`: The reference group for the binary analysis, default is `1`
-   `Log2FC_cutoff`: The cutoff for the log2 fold change of the binary analysis, default is `0.585`
-   `estimate_cutoff`: Effect size threshold for continuous traits, default is `0.2`
-   `probs`: Quantile cutoff for cell classification, default is `0.2`

**usage**:

```{r scPP_screening}
# This will take several hours
scpp_result = Screen(
  matched_bulk = your_matched_bulk,
  sc_data = A_Seurat_object,
  phenotype = your_matched_phenotype,
  label_type = "TP53", # The filtering labels are stored in the `@misc` 
  screen_method = "scpp",
  phenotype_class = "binary",
)
```

**returning structure**: A list containing:

-   `scRNA_data`: A Seurat object after screening

### 3.5 (Optional) Merge screening results

If you have performed multiple screening methods one the same data, you can use the function `MergeResult` to merge the results of these methods. The Seurat object or a results list from `Screen` is accepted.

```{r merge_screening_results}
merged_seurat=MergeResult(
    your_scissor_result, 
    your_scPAS_result, 
    your_scAB_result, 
    your_scPP_result
)

# * mixed input form is alse supported 

merged_seurat=MergeResult(
    your_scissor_result$scRNA_data, 
    your_scPAS_result$scRNA_data, 
    your_scAB_result, 
    your_scPP_result,
)

```

This function performs a simple task of consolidating screening results into the Seurat object's `meta.data` slot and returning the updated object. Please note that the intermediate data (e.g., `scissor_result$reliability.test` and `scab_result$scAB_result`) will not be preserved in this process.

------------------------------------------------------------------------

## 4. Visualization

Here we provide some visualization methods for the screening results.

### 4.1 UMAP for screening results

**example**:

Suppose you have performed `scissor` algorithm screening on your Seurat object and wish to examine the distribution across different celltypes and patient, you may reference and use the following code:

```{r umap_exmaple}
library(patchwork)
library(zeallot)

c(celltype_umap, patient_umap, scissor_umap) %<-%
    purrr::map(
        c("celltype", "patient", "scissor"),
        ~ Seurat::DimPlot(
            your_seurat_obj,
            group.by = .x,
            label.size = 6,
            pt.size = 0.6,
            reduction = "umap"
        ) +
            ggplot2::ggtitle(.x)
    )

# * Show
celltype_umap | patient_umap | scissor_umap
```

This will generate three UMAP plots separately.

Or suppose you have performed `scPAS` screening on your Seurat object and want to visualize the distribution of prediction confidence scores, you may reference and use the following code:

```{r umap_exmaple2}
library(patchwork)
library(zeallot)

c(scPAS_Pvalue_umap, scPAS_NRS_umap) %<-%
    purrr::map(
        c("scPAS_Pvalue", "scPAS_NRS"),
        ~ Seurat::FeaturePlot(
            object = your_seurat_obj,
            features = .x,
            label.size = 6,
            pt.size = 0.6,
            label = TRUE
        ) +
            ggplot2::ggtitle(.x) +
            theme(legend.position = "right")
    )

# * Show
scPAS_Pvalue_umap | scPAS_NRS_umap
```

This will generate two plots, one for each feature specified in `feature`.

**helpful documentation**:

[Seurat::DimPlot - https://satijalab.org/seurat/reference/DimPlot.html](https://satijalab.org/seurat/reference/DimPlot.html)

[Seurat::FeaturePlot - https://satijalab.org/seurat/reference/FeaturePlot.html](https://satijalab.org/seurat/reference/FeaturePlot.html)

### 4.2 Stack bar plot for screening results

Key parameters for `ScreenFractionPlot`:

-   `seurat_obj`: A Seurat object after screening.
-   `group_by`: Used to specify the column of the meta.data in `seurat_obj`. The plot results will be grouped by this parameter.
-   `screen_type`: Screening algorithm used before. (case-sensitive, e.g., "scissor" for Scissor results)
-   `show_null`: Logical whether to show groups with zero cells (default: FALSE).
-   `plot_color` Custom color palette (named vector format):
    -   Required names: "Positive", "Negative", "Neutral", "Other"
    -   Default: c("Neutral"="#CECECE", "Other"="#CECECE", "Positive"="#ff3333", "Negative"="#386c9b")

Suppose you have already performed the `scPAS` algorithm screening on your Seurat object, and you want to check the proportion of positive cells across different patients. You can refer to and use the following code:

```{r stack_bar_plot_example}
# based on `ggplot2`
plot <- ScreenFractionPlot(
   screened_seurat = your_seurat_obj,
   group_by = "patient", 
   screen_type = "scPAS",
   plot_title = "scPAS Screening Results"
)
```

The order of the groups is determined by the proportion of **Positive** cells within each group.

Use `?ScreenFractionPlot` in R to see more details.


### 4.3 Venn diagram for screening results

`ggVennDiagram` is used to generate a Venn diagram for the screening results. Suppose you have performed some of the screening algorithms on your Seurat object, and you want to check the overlap of the cells selected by each algorithm. You can refer to and use the following code:

**example**:

```{r venn_diagram_example}
library(ggVennDiagram)

# * get the cell vectors
scissor_pos <- colnames(scissor_result$scRNA_data)[
    which(scissor_result$scRNA_data$scissor == "Positive")
]
scab_pos <- colnames(scab_result$scRNA_data)[
    which(scab_result$scRNA_data$scAB == "Positive")
]
scpas_pos <- colnames(scpas_result$scRNA_data)[
    which(scpas_result$scRNA_data$scPAS == "Positive")
]
scpp_pos <- colnames(scissor_result$scRNA_data)[
    which(scpp_result$scRNA_data$scPP == "Positive")
]
all_cell <- colnames(your_seurat_obj) # this obj can be changed to other

# * create a list of cell vectors
pos_venn = list(
    scissor = scissor_pos,
    scpas = scpas_pos,
    scab = scab_pos,
    scpp = scpp_pos,
    all_cells = all_cells
)

set.seed(123)

venn_plot = ggVennDiagram::ggVennDiagram(
    x = pos_venn,
    # * the names shown on the diagram
    category.names = c(
        "Scissor",
        "scPAS",
        "scAB",
        "scPP",
        "All cells"
    ),
    # * the colors of each group
    set_color = c(
        "#a33333ff",
        "#37ae00ff", 
        "#2a2a94ff",
        "#9c8200ff",
        "#008383ff"
    )
) +
    ggplot2::scale_fill_gradient(low = "white", high = "#ffb6b6ff") +
    ggplot2::ggtitle("Screening Venn Diagram")
```

**helpful documentation**:

[ggVennDiagram - https://gaospecial.github.io/ggVennDiagram/](https://gaospecial.github.io/ggVennDiagram/)

------------------------------------------------------------------------

## 5. Example {#example}

Here we use the example data to demonstrate how to use the functions in `SigBridgeR` to screen cells associated with phenotype.

```{r example}
library(SigBridgeR)

```

------------------------------------------------------------------------

## 6. Other function details

### 6.1 Add miscellaneous information to the Seurat object

-   `AddMisc()` : Add miscellaneous information to the Seurat object. Support for adding multiple attributes to the `SeuratObject@misc` slot simultaneously.

```{r add_misc_example}
# basic usage
seurat_obj <- AddMisc(seurat_obj, "QC_stats" = qc_df)

# Auto-incrementing example when `cover` set to FALSE
seurat_obj <- AddMisc(seurat_obj, markers = markers1)
seurat_obj <- AddMisc(seurat_obj, markers = markers2, cover=FALSE)

# Add multiple attributes to the `SeuratObject@misc` slot simultaneously
seurat_obj <- AddMisc(seurat_obj, markers1 = markers1, markers2 = markers2)
```

Use `?AddMisc` in R to see more details.

### 6.2 Calculate the variance of each row in a matrix

-   `rowVars()` : Calculate the variance of each row in a matrix.

```{r row_vars_example}
 # Basic usage with a matrix
 mat <- matrix(1:12, nrow = 3)
 rowVars(mat)

 # With missing values
 mat[1, 2] <- NA
 mat[2, 3] <- NA
 rowVars(mat, na.rm = TRUE)   # Excludes NAs
 rowVars(mat, na.rm = FALSE)  # Includes NAs (returns NA for affected rows)

 # With a data frame
 df <- data.frame(
   a = c(1, 4, 7),
   b = c(2, 5, 8),
   c = c(3, 6, 9)
 )
 rowVars(df)

 # Edge case: single column (variance is 0)
 single_col <- matrix(1:3, ncol = 1)
 rowVars(single_col)  # Returns NaN due to division by 0
```

------------------------------------------------------------------------

## 7. References

Identifying phenotype-associated subpopulations by integrating bulk and single-cell sequencing data. Nature Biotechnology (2021). https://doi.org/10.1038/s41587-021-01091-3. Duanchen Sun, Xiangnan Guan, Amy E. Moran, Ling-Yun Wu, David Z. Qian, Pepper Schedin, Mu-Shui Dai, Alexey V. Danilov, Joshi J. Alumkal, Andrew C. Adey, Paul T. Spellman and Zheng Xia