---
title: "Troubleshooting"
author: "Exceret"
date: '`r Sys.Date()`'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Troubleshooting}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Overview

This vignette provides solutions to common problems you might encounter when using this package. If you cannot find your problem here, please file an issue on our GitHub repository.

------------------------------------------------------------------------

> ## Error in normalize.quantiles(dataset0) : ERROR; return code from pthread_create() is 22

To solve this problem, you need to install `preprocessCore` without threading support. Try:

```{shell}
git clone https://github.com/bmbolstad/preprocessCore.git
cd preprocessCore
R CMD INSTALL --configure-args="--disable-threading"  .
```

or

```{r}
BiocManager::install(
  "preprocessCore",
  configure.args = "--disable-threading",
  force = TRUE
)
```

See [bioconductor_docker/issues/22](https://github.com/Bioconductor/bioconductor_docker/issues/22), [Scissor/issues/15](https://github.com/sunduanchen/Scissor/issues/15) for more details.

------------------------------------------------------------------------

> ## Error at alpha=0.05:subscript out of bounds
> ## Error in `Scissor.v5.optimized()`:
> ## ! object 'fit0' not found

This is due to a mismatch in the dimensions of the bulk expression data and the phenotype data. Please ensure they share a common sample source.

To check dimension mismatch：
```{r}
ncol(your_bulk_data) == nrow(your_phenotype_data) # should be TRUE

(unique(colnames(your_bulk_data)) ==
  unique(rownames(
    ncol(your_bulk_data) == nrow(your_phenotype_data)
  ))) |>
  all() # should be TRUE
```

if you still got error, try to reduce the PCA dimension.

```{r}

```